Joint Training of Classification and Similarity Models for \\ Intention Detection in Task-specific Chatbot

### 2020-09-10 chatbot_classification/aaai_2021/experiments.tex
modified:   experiments.tex

\subsection{Implementation Details}
For  our  SFC  systems,  we  use RoBERTa-large as the pretrained model for both
classification  task  and  sentence-pair similarity task. We fine-tune
our  SFC  system  on  our datasets with max sequence length of 128,
learning  rate  of 1.5e-5 for RoBERTa-large pretrained model and learning rate
of  5e-4  for  task-specific  layer  with polynomial decay and Adam optimizer.
Besides,  we  set  the  max number of the epoch to 100 and save the best model on
validation  set based on testing result in weighted F1 score
\footnote{In the multi-class and multi-label case, this is the average of the
F1 score of each class with weighting depending on the numbers in each class.}.
We report the F1 score as the main evaluation measure for all experiments.

@@

\subsection{Result Analysis}
All  results  in  F1  score  on  the  five  datasets with different models and
configurations are showed in Table \ref{tbe:table2}.

@@

\subsubsection*{Settings  of  hyperparameters} 
Finally, we analyze the effect brought
by  different  settings  of  hyperparameters,  see  Table \ref{tbe:table3}.

We  conduct  experiments on 5 different settings of hyperparameters, which are
the  number of candidate class number $K$ and the number of sentence pairs $P$
for  each  class,  on  ITG  and Amazon-670K datasets to find the most suitable
setting  of  these  2 hyperparameters. We control the total number of sentence
pairs  sampled for each user query into about the same level of amount(50-60).
Through  analyzing the experimental results shown in Table \ref{tbe:table3}, we
find  that the best setting of hyperparameters might be different for datasets
of  different  data  size.  The  class label number of ITG and Amazon-670k are
similar  in  our  experimental setting, which is around 250. However the total
amount of data points of ITG is approximately 2 times larger than Amazon-670k.
Therefore,  the  setting of $K=5$ and $P=10$ is good enough for ITG since most
of  the  classes  contains  over 10 data points. However, for Amazon-670k, the
amount  of  data  sample  for  each  class  is  scarce, thus, we may need more
candidate  classes to sample enough effective sentence pairs for sentence-pair
model  layer  of  SFC.  In this way, the setting of $K=10$ and $P=5$ becomes a
good choice. However, in spite of the effect on evaluation performance brought
by different settings of hyperparameters, joint SFC still steadily outperforms
two-stage  SFC  by  0.41  percents  in  overall  average  F1 score  on  ITG and
Amazon-670k datasets.

In  conclusion, to the best of our knowledge, these experimental results place
joint  SFC as the best performing model on 5 diverse experimental datasets for
text   classification   task,   especially   when   it's   under  low-resource
task-specific conversational chatbot scenario.

>>>>

\subsection{Implementation Details}
For  our  SFC  systems,  we  use RoBERTa-large as the pretrained model for both
classification  task  and  sentence-pair similarity task. We fine-tune
our  SFC  system  on  our datasets with max sequence length of 128,
learning  rate  of 1.5e-5 for RoBERTa-large pretrained model and learning rate
of  5e-4  for  task-specific  layer  with polynomial decay and Adam optimizer.

@@

\subsection{Result Analysis}
We  report  the F1 score \footnote{In the multi-class and multi-label case, this
is  the  average  of  the F1 score of each class with weighting depending on the
numbers  in  each class.}. as the main evaluation measure for all experiments in
Table \ref{tbe:table2}.

@@

\subsubsection*{Settings  of  hyperparameters} 
In  Table \ref{tbe:table3}, we explore the influence from hyperparameters, which
are  the  number  of  candidate  class  labels $K$ in stage 1, and the number of
sampled  sentence  pairs  for  each class $P$ in stage 2, on ITG and Amazon-670K
datasets.  As we control the total number of sampled sentence pairs to about 50 to 60, we
roughly obatin five combinations of hyperparameters.

We find  that the best setting of hyperparameters is different from datasets
of  different  data  size.  The  class label number of ITG and Amazon-670k are
similar  in  our  experimental setting, which is around 250. However the total
amount of data points of ITG is approximately 2 times larger than Amazon-670k.
Therefore,  the  setting of $K=5$ and $P=10$ is good enough for ITG since most
of  the  classes  contains  over 10 data points. However, for Amazon-670k, the
amount  of  data  sample  for  each  class  is  scarce, thus, we may need more
candidate  classes to sample enough effective sentence pairs for sentence-pair
model  layer  of  SFC.  In this way, the setting of $K=10$ and $P=5$ becomes a
good choice.

However,  in  spite of the effect on evaluation performance brought by different
settings  of hyperparameters, joint SFC still steadily outperforms two-stage SFC
by  0.41  percent  points  in  overall  average  F1 score on ITG and Amazon-670k
datasets.
